Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-11 WRITEUP/ms.tex
minor text edit

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
Before accounting for contribution of the stellar component to the gravitational potential, 
most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).
Fragmentation are expected in regions of low Toomre $Q_{\rm eff}$ values.
Further interpretation and implication of this is discussed in \Sec{origin}.

>>>>

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
Before accounting for the thickness of the disk and the 
contribution of the stellar component to the gravitational potential, 
most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).
Fragmentation are expected in regions of low Toomre $Q_{\rm eff}$ values.
Further interpretation and implication of this is discussed in \Sec{origin}.
